---
title: "stas_N398"
author: "chchch"
date: "2025-09-17"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(readr)
library(tidyverse)
library(ggplot2)
library(stringr)
library(gridExtra)
library(ggpattern)
library(openxlsx)
library(ggpubr)
library(lme4)
library(ggsignif)
library(glmmTMB)
library(ggeffects)
library(mediation)
library(vcd)

check_overdispersion <- function(model) {
  rdf <- df.residual(model)
  rp <- residuals(model, type = "pearson")
  dispersion <- sum(rp^2) / rdf
  return(dispersion)
}

extract_lmer_coefs <- function(model) {
  coefs <- data.frame(coef(summary(model)))
  coefs <- coefs %>%
    mutate(
      Estimate = round(Estimate, 5),
      Std..Error = round(Std..Error, 5),
      t.value = round(t.value, 4),
      p.z = ifelse(
        2 * (1 - pnorm(abs(t.value))) < 0.001, "<.001",
        ifelse(
          2 * (1 - pnorm(abs(t.value))) < 0.01, "<.01",
          ifelse(
            2 * (1 - pnorm(abs(t.value))) < 0.05, "<.05",
            round(2 * (1 - pnorm(abs(t.value))), 4)
          )
        )
      )
    )
  return(coefs)
}
```

=================================================================================

### Data pre-processing: N=398
```{r message=FALSE, warning=FALSE}
# All inputs used below (except the 3 explicitly marked "not required") are
# shipped in this repository under dataset/. See README.md for the full
# pipeline and for how each file is produced upstream.

audio <- read_csv("../dataset/audio_cluster_54_k5_v1.csv",
                      locale = locale(encoding = "utf8"))

audio1 <- audio %>%
  dplyr::select(keycode, kmeans_cluster) %>%
  rename(cluster_a = kmeans_cluster)

audio_raw <- read_csv("../dataset/features_raw_251001.csv")
audio_raw1 <- audio_raw %>%
  dplyr::select(keycode, mean_f0, std_f0, VUV, speaking_rate_w, MFCC0, F1, F2,
                falling_ratio, rising_ratio, `rising-falling_ratio`, `falling-rising_ratio`,
                arousal, valence, std_arousal, std_valence)

visual <- read_csv("../dataset/visual_cluster_54_k6_v1.csv",
                   locale = locale(encoding = "utf8"))
visual1 <- visual %>%
  dplyr::select(kmeans_cluster, keycode) %>%
  rename(cluster_v = kmeans_cluster)

text <- read_csv("../dataset/text_cluster_33_k4_v_auto.csv")
text1 <- text %>%
  dplyr::select(keycode, kmeans_cluster,
                Analytic, Clout, Authentic, affiliation, achieve, power, emo_pos,
                emo_anx, emo_anger, emo_sad, swear, prosocial, polite, conflict,
                we, they, moral, risk, motion) %>%
  rename(cluster_t = kmeans_cluster)

# Base table combined1/combined2 below are built from
# (party/state/name/win/gender/...).
combined <- read_csv("../dataset/visual_audio_cluster_54_k5_v1.csv",
                    locale = locale(encoding = "utf8"))

# Third-party NYTimes polling data -- check licensing before redistributing
# this file further if you did not already confirm you may do so.
poll <- read_csv("../dataset/Poll_NYTimes_241001-241104_v2.csv",
                    locale = locale(encoding = "utf8"))

poll1 <- poll %>%
  group_by(state, date) %>%
  mutate(poll_norm = poll/sum(poll))

issue <- read_csv("../dataset/word_data_398.csv",
                      locale = locale(encoding = "utf8"))
issue1 <- issue %>%
  dplyr::select(keycode, topic)

# NOT included in this repository, but also NOT required to reproduce `data`
# below: the inner_join(length1, ...) a few chunks down is commented out, so
# length1 is currently dead code. Safe to skip unless you re-enable that join.
length <- read_csv("video_length_N585.csv",
                      locale = locale(encoding = "utf8"))
length1 <- length %>%
  mutate(
    video_len = as.character(video_len),  # ensure character
    length_sec = sapply(strsplit(video_len, ":"), function(x) {
      parts <- as.numeric(x)
      if (length(parts) == 3) {
        parts[1]*3600 + parts[2]*60 + parts[3]
      } else if (length(parts) == 2) {
        parts[1]*60 + parts[2]
      } else {
        as.numeric(parts)
      }
    }))

sentiment <- read_csv("../dataset/ig_video_N398_post,comment,whisper_cluster_sentiment_statistics(before0109)_0716_v3.csv")
sentiment1 <- sentiment %>%
  dplyr::select(-caption) %>%
  dplyr::select(comment_count, comment_score_pos, comment_score_neg, comment_score_neu, keycode)

# NOT included in this repository, but also NOT required to reproduce `data`
# below: all_comments is read but never referenced again after this point.
all_comments <- read_csv("ig_video_N583_comments_bert_TimeLMs_sentiment_results_250716_updated.csv")


pop <- read_csv("../dataset/combined_241001-241104_N398_caption_post_populism.csv",
                locale = locale(encoding = "big5"))

pop1 <- pop %>%
  dplyr::select(-text, -date, -name, -state, -party) %>%
  mutate(text_pop = ifelse(text_num_matched_roots == 0, 0, 1)) %>%
  mutate(caption_pop = ifelse(caption_num_matched_roots == 0, 0, 1)) %>%
  dplyr::select(text_pop, caption_pop, keycode)

populism <- read_csv("../dataset/labeled_populism_v38_N398.csv")

populism1 <- populism %>%
  mutate(people_centrism = ifelse(centr > 0.5, 1, 0)) %>%
  mutate(anti_elitism = ifelse(elite > 0.5, 1, 0)) %>%
  mutate(left_wing = ifelse(left > 0.5, 1, 0)) %>%
  mutate(right_wing = ifelse(right > 0.5, 1, 0)) %>%
  mutate(party_b = ifelse(party == "Republican", 1, 0)) %>%
  dplyr::select(people_centrism, anti_elitism, left_wing, right_wing, elite, centr, left, right, keycode) %>%
  mutate(popp = ifelse(people_centrism == 1 & anti_elitism == 1, "both",
                       ifelse(people_centrism == 0 & anti_elitism == 1, "elite",
                              ifelse(people_centrism == 1 & anti_elitism == 0, "centr",
                                     "none")))) %>%
  mutate(popornot = ifelse(popp == "none", 0, 1))
  #dplyr::select(elite, centr, left, right, keycode)

# NOT included in this repository, but also NOT required to reproduce `data`
# below: the inner_join(objects1, ...) a few chunks down is commented out, so
# objects1 is currently dead code. Safe to skip unless you re-enable that join.
objects <- read_csv("ig_videos_20240901-20241104_N583_yolov11_Objects365_counts.csv")
non_object_cols <- c("keycode", "max_frame")
objects1 <- objects %>%
  dplyr::select(-video_name) %>%
  mutate(across(
    .cols = -all_of(non_object_cols),
    .fns = ~ .x / max_frame,
    .names = "{.col}"
  ))

# Note: dataset/ also has ig_video_visualValid_N584_0901-1104_zscoreEngagement_0328.csv,
# a different snapshot (different N and calibration date) of the same
# underlying table -- this is the correct/matching one for this analysis.
engagement <- read_csv("../dataset/ig_video_visualValid_N583_0901-1104_zscoreEngagement_250909.csv")
engagement1 <- engagement %>%
  dplyr::select(`7days_followers`, `7days_followers_zscore`, post_date, follower_date,
                post_likes_zscore, post_comments_zscore,
                engagement_rate, engagement_rate_zscore, likes_by_follower, comments_by_follower, 
                likes_by_follower_zscore, comments_by_follower_zscore, keycode) 

# combined data
combined1 <- combined %>%
  dplyr::select(-issue_label, -issue_name, -hierarchical_cluster_0.5, 
                -post_likes_zscore, -post_comments_zscore,
                -engagement_rate, -engagement_rate_zscore, -likes_by_follower, -comments_by_follower,
                -likes_by_follower_zscore, -comments_by_follower_zscore,
                -mean_f0,- std_f0, -VUV, -speaking_rate_w, -MFCC0, -F1, -F2, 
                -falling_ratio, -rising_ratio, -`rising-falling_ratio`, -`falling-rising_ratio`,
                -arousal, -valence, -std_arousal, -std_valence) %>%
  mutate(name = as.factor(name)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(win = as.factor(win)) %>%
  mutate(state = as.factor(state)) %>%
  rename(cluster_va = kmeans_cluster) %>%
  mutate(keycode = as.factor(keycode)) 

combined2 <- combined1 %>% 
  dplyr::left_join(audio1, by = "keycode") %>%
  dplyr::left_join(audio_raw1, by = "keycode") %>%
  dplyr::left_join(visual1, by = "keycode") %>%
  dplyr::left_join(text1, by = "keycode") %>%
  dplyr::left_join(issue1, by = "keycode") %>%
  dplyr::left_join(populism1, by = c("keycode")) %>%
  dplyr::inner_join(engagement1, by = c("keycode")) %>%
  #dplyr::left_join(pop1, by = "keycode") %>%
  #dplyr::inner_join(objects1, by = "keycode") %>%
  dplyr::inner_join(poll1, by = c("state", "date", "name", "poll")) %>%
  #dplyr::inner_join(length1, by = c("state", "date", "name", "party", "keycode")) %>%
  dplyr::inner_join(sentiment1, by = c("keycode"))
  

data <- combined2 %>%
  mutate(cluster_v = ifelse(cluster_v == "0", "Excited", ifelse(cluster_v == "1", "Frowning", 
                                                         ifelse(cluster_v == "2", "Expressive",
                                                                ifelse(cluster_v == "3", "Serious", 
                                                                       ifelse(cluster_v == "4", "Still",
                                                                              "Cheerful")))))) %>%
  mutate(cluster_a = ifelse(cluster_a == "0", "Warm", ifelse(cluster_a == "1", "Sharp", 
                                                         ifelse(cluster_a == "2", "Rapid",
                                                                ifelse(cluster_a == "3", "Somber", 
                                                                              "Energetic")))))  %>%
  mutate(cluster_va = ifelse(cluster_va == "0", "Stony Warm", ifelse(cluster_va == "1", "Concerned Articulate", 
                                                         ifelse(cluster_va == "2", "Cheerful Energetic",
                                                                ifelse(cluster_va == "3", "Responsive Rapid",
                                                                       "Negative Depressed")))))  %>%
  mutate(cluster_t = ifelse(cluster_t == "0", "authentic", ifelse(cluster_t == "1", "polite",
                                                         ifelse(cluster_t == "2", "anxious", "combative"))))  %>%
  mutate(cluster_va = as.factor(cluster_va)) %>%
  mutate(cluster_v = as.factor(cluster_v)) %>%
  mutate(cluster_t = as.factor(cluster_t)) %>%
  mutate(cluster_a = as.factor(cluster_a)) 
```

```{r}
liwc <- read_csv("../dataset/labeled_populism_v38_N398 - LIWC Analysis.csv")
```

#### transposed table of features
```{r}
audio_features <- c("mean_f0", "std_f0", "VUV", "speaking_rate_w", "MFCC0", "F1", "F2", 
                    "falling_ratio", "rising_ratio", "rising-falling_ratio", "falling-rising_ratio",
                    "arousal", "valence", "std_arousal", "std_valence")

visual_features <- c("AU01_mean", "AU02_mean", "AU04_mean", "AU06_mean", "AU12_mean", 
                      "AU15_mean", "AU20_mean", "AU25_mean",
                      "pitch_count_percentage", "roll_count_percentage", "yaw_count_percentage",
                     "valence_mean", "valence_std", "arousal_mean", "arousal_std")

textual_features <- c("Analytic", "Clout", "Authentic", "affiliation", "achieve", "power", "emo_pos",
                      "emo_anx", "emo_anger", "emo_sad", "swear", "prosocial", "polite", "conflict",
                      "we", "they", "moral", "risk", "motion")

data_v <- data %>%
  dplyr::select(cluster_v, visual_features) %>%
  group_by(cluster_v) %>%
  reframe(N = n(), percentage = round((N/398)*100, 2),
          across(all_of(visual_features), ~ round(mean(.x), 2)))

cols <- c("V1","V2","V3","V4","V5","V6")

transposed_v <- as.data.frame(t(data_v)) %>%
  mutate(
    All  = rowSums(across(all_of(cols), ~ as.numeric(.x)), na.rm = TRUE),
    mean = round(rowMeans(across(all_of(cols), ~ as.numeric(.x)), na.rm = TRUE), 2)
  ) %>%
  tibble::rownames_to_column("feature")

 data_a <- data %>%
  dplyr::select(cluster_a, audio_features) %>%
  group_by(cluster_a) %>%
  reframe(N = n(), percentage = round((N/398)*100, 2),
          across(all_of(audio_features), ~ round(mean(.x), 2)))

cols <- c("V1","V2","V3","V4","V5")

transposed_a <- as.data.frame(t(data_a)) %>%
  mutate(
    All  = rowSums(across(all_of(cols), ~ as.numeric(.x)), na.rm = TRUE),
    mean = round(rowMeans(across(all_of(cols), ~ as.numeric(.x)), na.rm = TRUE), 2)
  ) %>%
  tibble::rownames_to_column("feature")

data_t <- data %>%
  dplyr::select(cluster_t, textual_features) %>%
  group_by(cluster_t) %>%
  reframe(N = n(), percentage = round((N/398)*100, 2),
          across(all_of(textual_features), ~ round(mean(.x, na.rm = TRUE), 2)))

cols <- c("V1","V2","V3","V4")

transposed_t <- as.data.frame(t(data_t)) %>%
  mutate(
    All  = rowSums(across(all_of(cols), ~ as.numeric(.x)), na.rm = TRUE),
    mean = round(rowMeans(across(all_of(cols), ~ as.numeric(.x)), na.rm = TRUE), 2)
  ) %>%
  tibble::rownames_to_column("feature")

# write_csv(transposed_a, "audio_features_mean_N398_251002.csv")
# write_csv(transposed_t, "text_features_mean_N398_251002.csv")
# write_csv(transposed_v, "visual_features_mean_N398_251002.csv")
```



### style and popornot
#### v + a + t + topic
```{r}
data1 <- data %>%
  #filter(party != "Republican") %>%
  mutate(party = as.factor(party)) %>%
  mutate(gender = as.factor(gender)) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(popornot = relevel(popornot, "0")) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- glmer(popornot ~ cluster_v + cluster_a + cluster_t + topic + party + gender + (1 | name), 
               data = data1, family = "binomial")
summary(model)
```

#### va + t + topic
```{r}
data1 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(gender = as.factor(gender)) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(popornot = relevel(popornot, "0")) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic")) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- glmer(popornot ~ cluster_va + cluster_t + topic + party + gender + (1 | name), 
               data = data1, family = "binomial")
summary(model)
```

#### v + a + va + t
```{r}
data1 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(gender = as.factor(gender)) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(popornot = relevel(popornot, "0")) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic")) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- glmer(popornot ~ cluster_v + cluster_a + cluster_va + cluster_t + party + gender + (1 | name), 
               data = data1, family = "binomial")
summary(model)
```

#### va + t
```{r}
data1 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(gender = as.factor(gender)) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(popornot = relevel(popornot, "0")) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic")) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- glmer(popornot ~ cluster_va + cluster_t + party + gender + (1 | name), 
               data = data1, family = "binomial")
summary(model)
```

#### v + a + t
```{r}
data1 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(gender = as.factor(gender)) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(popornot = relevel(popornot, "0")) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic")) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- glmer(popornot ~ cluster_v + cluster_a + cluster_t + party + gender + (1 | name), 
               data = data1, family = "binomial")
summary(model)
```

### Populism

#### PopBERT
```{r}
data %>%
  group_by(popp, party) %>%
  count()

tab_style  <- with(data, table(popp, cluster_v))
chi <- chisq.test(tab_style)
chi
chi$stdres

```

##### stat models
```{r}
# left
model <- lmer(left ~ party + (1|name), data = data)
summary(model)
#extract_lmer_coefs(model)

# right
model <- lmer(right ~ party + (1|name), data = data)
summary(model)
#extract_lmer_coefs(model)

# centr
model <- lmer(centr ~ party + (1|name), data = data)
summary(model)
#extract_lmer_coefs(model)

# elite
model <- lmer(elite ~ party + (1|name), data = data)
summary(model)
#extract_lmer_coefs(model)
```

#### LIWC
```{r}
liwc_features <- c(
  "WC", "Analytic", "Clout", "Authentic", "Tone", "WPS", "BigWords", "Dic",
  "Linguistic", "function", "pronoun", "ppron", "i", "we", "you", "shehe", "they",
  "ipron", "det", "article", "number", "prep", "auxverb", "adverb", "conj", "negate",
  "verb", "adj", "quantity", "Drives", "affiliation", "achieve", "power", "Cognition",
  "allnone", "cogproc", "insight", "cause", "discrep", "tentat", "certitude", "differ",
  "memory", "Affect", "tone_pos", "tone_neg", "emotion", "emo_pos", "emo_neg", "emo_anx",
  "emo_anger", "emo_sad", "swear", "Social", "socbehav", "prosocial", "polite", "conflict",
  "moral", "comm", "socrefs", "family", "friend", "female", "male", "Culture", "politic",
  "ethnicity", "tech", "Lifestyle", "leisure", "home", "work", "money", "relig", "Physical",
  "health", "illness", "wellness", "mental", "substances", "sexual", "food", "death", "need",
  "want", "acquire", "lack", "fulfill", "fatigue", "reward", "risk", "curiosity", "allure",
  "Perception", "attention", "motion", "space", "visual", "auditory", "feeling", "time",
  "focuspast", "focuspresent", "focusfuture", "Conversation", "netspeak", "assent", "nonflu",
  "filler", "AllPunc", "Period", "Comma", "QMark", "Exclam", "Apostro", "OtherP", "Emoji"
)

names(populism1) <- make.names(names(populism1), unique = TRUE)

# Make sure column names are valid
liwc_features <- make.names(liwc_features)
```


##### left
```{r}
formula <- as.formula(
  paste("left ~ ", paste(liwc_features, collapse = " + "), "+ name")
)

model <- lm(formula, data = populism1)
summary(model)
```

##### right
```{r}
formula <- as.formula(
  paste("right ~ ", paste(liwc_features, collapse = " + "), "+ name")
)

model <- lm(formula, data = populism1)
summary(model)
```

##### centrm
```{r}
# Build the formula
formula <- as.formula(
  paste("centr ~ ", paste(liwc_features, collapse = " + "), "+ name")
)

model <- lm(formula, data = populism1)
summary(model)
```

##### elite
```{r}
# Build the formula
formula <- as.formula(
  paste("elite ~ ", paste(liwc_features, collapse = " + "), "+ name")
)

model <- lm(formula, data = populism1)
summary(model)
```

=================================================================================

### Populism or not
```{r}
data %>%
  group_by(popornot) %>%
  count()
```


#### Style and populism

##### Visual style
```{r}
tab_style  <- with(data, table(popornot, cluster_v))
chi <- chisq.test(tab_style)
chi
chi$stdres
```

##### audio style
```{r}
tab_style  <- with(data, table(popornot, cluster_a))
chi <- chisq.test(tab_style)
chi
chi$stdres
```

##### text style
```{r}
tab_style  <- with(data, table(popornot, cluster_t))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

##### audiovisual style
```{r}
tab_style  <- with(data, table(popornot, cluster_va))
chi <- chisq.test(tab_style)
chi
chi$stdres
```

##### topic
```{r}
tab_style  <- with(data, table(popornot, topic))
chi <- chisq.test(tab_style)
chi
chi$stdres
```



#### Party, populism, and styles
#### Republican
##### Visual style
```{r}
data1 <- data %>%
  filter(party == "Republican") %>%
  mutate(var = paste(party, popornot))

tab_style  <- with(data1, table(popornot, cluster_v))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

##### audio style
```{r}
data1 <- data %>%
  filter(party == "Republican") %>%
  mutate(var = paste(party, popornot))

tab_style  <- with(data1, table(popornot, cluster_a))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

##### text style
```{r}
data1 <- data %>%
  filter(party == "Republican") %>%
  mutate(var = paste(party, popornot))

tab_style  <- with(data1, table(popornot, cluster_t))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

##### audiovisual style
```{r}
data1 <- data %>%
  filter(party == "Republican") %>%
  mutate(var = paste(party, popornot))

tab_style  <- with(data1, table(popornot, cluster_va))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

##### topic
```{r}
data1 <- data %>%
  filter(party == "Republican") %>%
  mutate(var = paste(party, popornot))

tab_style  <- with(data1, table(popornot, topic))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

#### Democrats
##### Visual style
```{r}
data1 <- data %>%
  filter(party != "Republican") %>%
  mutate(var = paste(party, popornot))

tab_style  <- with(data1, table(popornot, cluster_v))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

##### audio style
```{r}
data1 <- data %>%
  filter(party != "Republican") %>%
  mutate(var = paste(party, popornot))

tab_style  <- with(data1, table(popornot, cluster_a))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

##### text style
```{r}
data1 <- data %>%
  filter(party != "Republican") %>%
  mutate(var = paste(party, popornot))

tab_style  <- with(data1, table(popornot, cluster_t))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

##### audiovisual style
```{r}
data1 <- data %>%
  filter(party != "Republican") %>%
  mutate(var = paste(party, popornot))

tab_style  <- with(data1, table(popornot, cluster_va))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

##### topic
```{r}
data1 <- data %>%
  filter(party != "Republican") %>%
  mutate(var = paste(party, popornot))

tab_style  <- with(data1, table(popornot, topic))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi
chi$stdres
```

#### Party and populism
```{r}
tab_style  <- with(data, table(popornot, party))
chi <- chisq.test(tab_style)
chi$stdres
```

#### Party and style
##### visual
```{r}
tab_style  <- with(data, table(cluster_v, party))
chi <- chisq.test(tab_style)
chi$stdres
```

##### audio
```{r}
tab_style  <- with(data, table(cluster_a, party))
chi <- chisq.test(tab_style)
chi$stdres
```

##### text
```{r}
tab_style  <- with(data, table(cluster_t, party))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi$stdres
```

##### audiovisual
```{r}
tab_style  <- with(data, table(cluster_va, party))
chi <- chisq.test(tab_style)
chi$stdres
```

##### topic
```{r}
tab_style  <- with(data, table(topic, party))
chi <- chisq.test(tab_style)
chi$stdres
```


#### binary regression
##### visual
```{r}
data1 <- data %>%
  #filter(party != "Republican") %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

model <- glmer(popornot ~ cluster_v + gender + party + (1|name), data = data1, family = "binomial")
#model <- glm(popornot ~ cluster_v+gender + name, data = data1, family = "binomial")
summary(model)
```
##### audio
```{r}
data1 <- data %>%
  #filter(party != "Republican") %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

model <- glmer(popornot ~ cluster_a + gender + party + (1|name), data = data1, family = "binomial")
#model <- glm(popornot ~ cluster_a + gender, data = data1, family = "binomial")
summary(model)
```

##### audiovisual
```{r}
data1 <- data %>%
  #filter(party != "Republican") %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

model <- glmer(popornot ~ cluster_va + gender + party + (1|name), data = data1, family = "binomial")
summary(model)
```

##### text
```{r}
data1 <- data %>%
  #filter(party != "Republican") %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- glmer(popornot ~ cluster_t + gender + party + (1|name), data = data1, family = "binomial")
summary(model)
```

##### topic
```{r}
data1 <- data %>%
  #filter(party != "Republican") %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

model <- glmer(popornot ~ topic + gender + party + (1|name), data = data1, family = "binomial")
summary(model)
```

=================================================================================
### Populism distribution
```{r}
data %>%
  mutate(ideo = ifelse(left_wing == 1 & right_wing == 1, "both",
                        ifelse(left_wing == 1 & right_wing == 0, "left", 
                                ifelse(left_wing == 0 & right_wing == 1, "right", "neutral")))) %>%
  group_by(popp, ideo) %>%
  count()
```


=================================================================================

### Populism and engagement
#### likes
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(popornot = as.factor(popornot))

combined3$popornot <- relevel(combined3$popornot, ref = "0")

#model_l <- glmmTMB(post_likes ~ popornot*party*gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ popornot*party*gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

```{r}
hist(combined3$likes_by_follower, breaks = 30, main = "Histogram", xlab = "likes_by_follower")
qqnorm(combined3$likes_by_follower)
qqline(combined3$likes_by_follower, col = "red")
```


#### comments
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  #filter(comment_count != 0) %>%
  mutate(popornot = as.factor(popornot))

combined3$popornot <- relevel(combined3$popornot, ref = "0")

#model_l <- glmmTMB(comment_count ~ popornot*party*gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ popornot*party*gender, data = combined3, family = tweedie(link = "log"))

summary(model_l)
```

#### comment sentiments
##### positive
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popornot = as.factor(popornot))

combined3$popornot <- relevel(combined3$popornot, ref = "0")

model_l <- lmer(comment_score_pos ~ popornot*party*gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```


##### neutral
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popornot = as.factor(popornot))

combined3$popornot <- relevel(combined3$popornot, ref = "0")

model_l <- lmer(comment_score_neu ~ popornot*party*gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```


##### negative
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popornot = as.factor(popornot))

combined3$popornot <- relevel(combined3$popornot, ref = "0")

model_l <- lmer(comment_score_neg ~ popornot*party*gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```


### RQ6 Engagements
#### likes
##### All
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model_l <- glmmTMB(likes_by_follower ~ cluster_v*popornot
                   +cluster_a*popornot
                   +cluster_t*popornot
                   +topic*popornot
                   +party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```
##### Populism = 1
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model_l <- glmmTMB(likes_by_follower ~ cluster_v+cluster_a+cluster_t+topic+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

##### Populism = 0
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model_l <- glmmTMB(likes_by_follower ~ cluster_v+cluster_a+cluster_t+topic+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```


#### comments
##### All
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model_l <- glmmTMB(comments_by_follower ~ cluster_v*popornot
                   +cluster_a*popornot
                   +cluster_t*popornot
                   +topic*popornot
                   +party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

##### Populism = 1
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model_l <- glmmTMB(comments_by_follower ~ cluster_v+cluster_a+cluster_t+topic+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

##### Populism = 0
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model_l <- glmmTMB(comments_by_follower ~ cluster_v+cluster_a+cluster_t+topic+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```
#### comment sentiments ratio
```{r}
# Add smoothing to avoid division by zero
epsilon <- 1e-6

data$sentiment_ratio <- data$comment_score_pos/ data$comment_score_neg
#data$sentiment_ratio1 <- (data$comment_score_pos + 1) / (data$comment_score_neg + 1)
data$sentiment_log_ratio <- log(data$comment_score_pos/ data$comment_score_neg)
# data$sentiment_log_ratio1 <- log((data$comment_score_pos + 1) / (data$comment_score_neg + 1))
# data$sentiment_log_ratio_e <- log((data$comment_score_pos + epsilon) / (data$comment_score_neg + epsilon))
hist(data$sentiment_log_ratio)
```

##### All
```{r}
data1 <- data %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

# model <- glm(sentiment_ratio1 ~ cluster_v*popornot
#                    +cluster_a*popornot
#                    +cluster_t*popornot
#                    +topic*popornot
#                    +party+gender, data = data1, family = Gamma(link = "log"))
# 
# summary(model)

model <- lmer(sentiment_log_ratio ~ cluster_v*popornot
                   +cluster_a*popornot
                   +cluster_t*popornot
                   +topic*popornot
                   +party + gender + (1|name), data = data1)

#extract_lmer_coefs(model)
summary(model)
```

##### Populism = 1
```{r}
data1 <- data %>%
  filter(popornot == 1) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- lmer(sentiment_log_ratio ~ cluster_v
                   +cluster_a
                   +cluster_t
                   +topic
                   +party + gender + (1|name), data = data1)

summary(model)
```

##### Populism = 0
```{r}
data1 <- data %>%
  filter(popornot == 0) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- lmer(sentiment_log_ratio ~ cluster_v
                   +cluster_a
                   +cluster_t
                   +topic
                   +party + gender + (1|name), data = data1)

summary(model)
```
### RQ7 Engagments (separated models )
#### likes
#### populism = 1
##### visual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

#model_l <- glmmTMB(post_likes ~ cluster_v+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ cluster_v+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

##### audio
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

#model_l <- glmmTMB(post_likes ~ cluster_a+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ cluster_a+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

##### text
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_t = relevel(cluster_t, "polite"))

#model_l <- glmmTMB(post_likes ~ cluster_t+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ cluster_t+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

#model_l <- glmmTMB(post_likes ~ cluster_va+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ cluster_va+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

##### topic
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

#model_l <- glmmTMB(post_likes ~ topic+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ topic+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

#### populism = 0
##### visual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

#model_l <- glmmTMB(post_likes ~ cluster_v+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ cluster_v+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

##### text
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_t = relevel(cluster_t, "polite"))

#model_l <- glmmTMB(post_likes ~ cluster_t+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ cluster_t+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

##### audio
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

#model_l <- glmmTMB(post_likes ~ cluster_a+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ cluster_a+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

#model_l <- glmmTMB(post_likes ~ cluster_va+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ cluster_va+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

##### topic
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

#model_l <- glmmTMB(post_likes ~ topic+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(likes_by_follower ~ topic+party+gender, data = combined3, family = Gamma(link = "log"))
summary(model_l)
```

#### comments

#### populism = 1


##### visual
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

#model_l <- glmmTMB(comment_count ~ cluster_v+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ cluster_v+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

##### audio
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

#model_l <- glmmTMB(comment_count ~ cluster_a+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ cluster_a+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```
##### text
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_t = relevel(cluster_t, "polite"))

#model_l <- glmmTMB(comment_count ~ cluster_t+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ cluster_t+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

#model_l <- glmmTMB(comment_count ~ cluster_va+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ cluster_va+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

##### topic
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

#model_l <- glmmTMB(comment_count ~ topic+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ topic+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

#### populism = 0
##### visual
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

#model_l <- glmmTMB(comment_count ~ cluster_v+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ cluster_v+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

##### audio
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

#model_l <- glmmTMB(comment_count ~ cluster_a+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ cluster_a+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

##### text
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_t = relevel(cluster_t, "polite"))

#model_l <- glmmTMB(comment_count ~ cluster_t+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ cluster_t+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

#model_l <- glmmTMB(comment_count ~ cluster_va+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ cluster_va+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

##### topic
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

#model_l <- glmmTMB(comment_count ~ topic+party+gender + (1 | name), data = combined3, family = nbinom2)
model_l <- glmmTMB(comments_by_follower ~ topic+party+gender, data = combined3, family = tweedie(link = "log"))
summary(model_l)
```

#### comment sentiment ratio
#### populism = 1
##### visual
```{r}
data1 <- data %>%
  filter(popornot == 1) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- lmer(sentiment_log_ratio ~ cluster_v + party + gender + (1|name), data = data1)
summary(model)
```

##### audio
```{r}
data1 <- data %>%
  filter(popornot == 1) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- lmer(sentiment_log_ratio ~ cluster_a + party + gender + (1|name), data = data1)
summary(model)
```

##### text
```{r}
data1 <- data %>%
  filter(popornot == 1) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- lmer(sentiment_log_ratio ~ cluster_t + party + gender + (1|name), data = data1)
summary(model)
```

##### audiovisual
```{r}
data1 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

model <- lmer(sentiment_log_ratio ~ cluster_va + party + gender + (1|name), data = data1)
summary(model)
```

##### topic
```{r}
data1<- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

model <- lmer(sentiment_log_ratio ~ topic+ party + gender + (1|name), data = data1)
summary(model)
```

#### populism = 0
##### visual
```{r}
data1 <- data %>%
  filter(popornot == 0) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- lmer(sentiment_log_ratio ~ cluster_v + party + gender + (1|name), data = data1)
summary(model)
```

##### audio
```{r}
data1 <- data %>%
  filter(popornot == 0) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- lmer(sentiment_log_ratio ~ cluster_a + party + gender + (1|name), data = data1)
summary(model)
```

##### text
```{r}
data1 <- data %>%
  filter(popornot == 0) %>%
  mutate(popornot = as.factor(popornot)) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting")) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful")) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic")) %>% 
  mutate(cluster_t = relevel(cluster_t, "polite"))

model <- lmer(sentiment_log_ratio ~ cluster_t + party + gender + (1|name), data = data1)
summary(model)
```

##### audiovisual
```{r}
data1 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

model <- lmer(sentiment_log_ratio ~ cluster_va + party + gender + (1|name), data = data1)
summary(model)
```

##### topic
```{r}
data1<- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

model <- lmer(sentiment_log_ratio ~ topic + party + gender + (1|name), data = data1)
summary(model)
```

##### positive
#### populism = 1
##### visual
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

model_l <- lmer(comment_score_pos ~ cluster_v+party+gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### audio
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

model_l <- lmer(comment_score_pos ~ cluster_a+party+gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### text
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_t = relevel(cluster_t, "polite"))

model_l <- lmer(comment_score_pos ~ cluster_t+party+gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

model_l <- lmer(comment_score_pos ~ cluster_va+party+gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### topic
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

model_l <- lmer(comment_score_pos ~ topic+party+gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

#### populism = 0
##### visual
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

model_l <- lmer(comment_score_pos ~ cluster_v+party+gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### audio
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

model_l <- lmer(comment_score_pos ~ cluster_a+party+gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### text
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_t  = as.factor(cluster_t)) %>%
  mutate(cluster_t = relevel(cluster_t, "polite"))

model_l <- lmer(comment_score_pos ~ cluster_t+party+gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

model_l <- lmer(comment_score_pos ~ cluster_va+party+gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### topic
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

model_l <- lmer(comment_score_pos ~ topic+party+gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### neutral
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popornot = as.factor(popornot))

combined3$popornot <- relevel(combined3$popornot, ref = "0")

model_l <- lmer(comment_score_neu ~ popornot*party*gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

#### populism = 1
##### visual
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

model_l <- glmmTMB(comment_count ~ cluster_v+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### audio
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

model_l <- glmmTMB(comment_count ~ cluster_a+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

model_l <- glmmTMB(comment_count ~ cluster_va+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### topic
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

model_l <- glmmTMB(comment_count ~ topic+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### populism = 0
##### visual
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

model_l <- glmmTMB(comment_count ~ cluster_v+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### audio
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

model_l <- glmmTMB(comment_count ~ cluster_a+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

model_l <- glmmTMB(comment_count ~ cluster_va+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### topic
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

model_l <- glmmTMB(comment_count ~ topic+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### negative
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popornot = as.factor(popornot))

combined3$popornot <- relevel(combined3$popornot, ref = "0")

model_l <- lmer(comment_score_neg ~ popornot*party*gender + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

#### populism = 1
##### visual
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

model_l <- glmmTMB(comment_count ~ cluster_v+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### audio
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

model_l <- glmmTMB(comment_count ~ cluster_a+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

model_l <- glmmTMB(comment_count ~ cluster_va+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### topic
```{r}
combined3 <- data %>%
  filter(popornot == 1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

model_l <- glmmTMB(comment_count ~ topic+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### populism = 0
##### visual
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_v  = as.factor(cluster_v)) %>%
  mutate(cluster_v = relevel(cluster_v, "Cheerful"))

model_l <- glmmTMB(comment_count ~ cluster_v+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### audio
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_a  = as.factor(cluster_a)) %>%
  mutate(cluster_a = relevel(cluster_a, "Energetic"))

model_l <- glmmTMB(comment_count ~ cluster_a+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(cluster_va  = as.factor(cluster_va)) %>%
  mutate(cluster_va = relevel(cluster_va, "Cheerful Energetic"))

model_l <- glmmTMB(comment_count ~ cluster_va+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### topic
```{r}
combined3 <- data %>%
  filter(popornot == 0) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic  = as.factor(topic)) %>%
  mutate(topic = relevel(topic, "Voting"))

model_l <- glmmTMB(comment_count ~ topic+party+gender + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

=================================================================================

### Populism and style

#### Visual style
```{r}
tab_style  <- with(data, table(popp, cluster_v))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi$stdres

#mosaic(tab_style, shade = TRUE, legend = TRUE)
```

#### audio style
```{r}
tab_style  <- with(data, table(popp, cluster_a))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi$stdres

#mosaic(tab_style, shade = TRUE, legend = TRUE)
```

#### audiovisual style
```{r}
tab_style  <- with(data, table(popp, cluster_va))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi$stdres

#mosaic(tab_style, shade = TRUE, legend = TRUE)
```

#### text
```{r}
tab_style  <- with(data, table(popp, cluster_t))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi$stdres

#mosaic(tab_style, shade = TRUE, legend = TRUE)
```

#### topic
```{r}
tab_style  <- with(data, table(popp, topic))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi$stdres

#mosaic(tab_style, shade = TRUE, legend = TRUE)
```

### Populism and styles in engagement
#### likes
##### visual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- glmmTMB(post_likes ~ popp*cluster_v + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


##### audio
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- glmmTMB(post_likes ~ popp*cluster_a + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


##### audiovisual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- glmmTMB(post_likes ~ popp*cluster_va + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### topic
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic = as.factor(topic)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")
combined3$topic <- relevel(combined3$topic, ref = "Candidate Strategies(mix)")

model_l <- glmmTMB(post_likes ~ popp*topic + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### comments
##### visual
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- glmmTMB(comment_count ~ popp*cluster_v + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### audio
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- glmmTMB(comment_count ~ popp*cluster_a + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### audiovisual
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- glmmTMB(comment_count ~ popp*cluster_va + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

##### topic
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic = as.factor(topic)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")
combined3$topic <- relevel(combined3$topic, ref = "Candidate Strategies(mix)")

model_l <- glmmTMB(comment_count ~ popp*topic + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### comment sentiments

##### positive
###### visual
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_pos ~ popp*cluster_v + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```


###### audio
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_pos ~ popp*cluster_a + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

###### audiovisual
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_pos ~ popp*cluster_va + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

###### topic
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic = as.factor(topic)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")
combined3$topic <- relevel(combined3$topic, ref = "Candidate Strategies(mix)")

model_l <- lmer(comment_score_pos ~ popp*topic + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### neutral
###### visual
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic = as.factor(topic)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_neu ~ popp*cluster_v + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

###### audio
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic = as.factor(topic)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_neu ~ popp*cluster_a + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

###### audiovisual
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic = as.factor(topic)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_neu ~ popp*cluster_va + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

###### topic
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic = as.factor(topic)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")
combined3$topic <- relevel(combined3$topic, ref = "Candidate Strategies(mix)")

model_l <- lmer(comment_score_neu ~ popp*topic + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

##### negative
###### visual
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_neg ~ popp*cluster_v + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

###### audio
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_neg ~ popp*cluster_a + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

###### audiovisual
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_neg ~ popp*cluster_va + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```

###### topic
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(topic = as.factor(topic)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")
combined3$topic <- relevel(combined3$topic, ref = "Candidate Strategies(mix)")

model_l <- lmer(comment_score_neg ~ popp*topic + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```


=================================================================================


### Party and populism
```{r}
tab_style  <- with(data, table(popp, party))
chi <- chisq.test(tab_style)
chi
chi$stdres
```

### Party, populism, and style
#### visual
```{r}
data1 <- data %>%
  filter(popp %in% c("both", "none")) %>%
  mutate(parpop = paste(party, popp))

tab_style  <- with(data1, table(parpop, cluster_v))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi$stdres
```

#### audio
```{r}
data1 <- data %>%
  filter(popp %in% c("both", "none")) %>%
  mutate(parpop = paste(party, popp))

tab_style  <- with(data1, table(parpop, cluster_a))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi$stdres
```

#### audiovisual
```{r}
data1 <- data %>%
  filter(popp %in% c("both", "none")) %>%
  mutate(parpop = paste(party, popp))

tab_style  <- with(data1, table(parpop, cluster_va))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi$stdres
```

#### topic
```{r}
data1 <- data %>%
  filter(popp %in% c("both", "none")) %>%
  mutate(parpop = paste(party, popp))

tab_style  <- with(data1, table(parpop, topic))
chi <- chisq.test(tab_style, simulate.p.value = TRUE, B = 1e5)
chi$stdres
```

### Party and populism in Engagement
#### likes
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- glmmTMB(post_likes ~ party*popp + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### comments
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- glmmTMB(comment_count ~ party*popp + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### comment sentiments
##### positive
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_pos ~ popp*party + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```


##### neutral
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_neu ~ popp*party + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```


##### negative
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party)) %>%
  mutate(popp = as.factor(popp))

combined3$popp <- relevel(combined3$popp, ref = "none")

model_l <- lmer(comment_score_neg ~ popp*party + (1 | name), data = combined3)
summary(model_l)
coefs <- extract_lmer_coefs(model_l)
coefs
```


### visualization
```{r}
ft <- ggarrange(t1, t2, t3, t4, nrow = 2, ncol = 2, common.legend = TRUE, legend="bottom")
annotate_figure(ft, , top = text_grob("Topic", face = "bold", size = 14))
#ggsave("figure_t.png", dpi = 600, width = 12, height = 8)
```


=================================================================================

### Party and style
#### visual
```{r}
tab_style  <- with(data, table(cluster_v, party))
chi <- chisq.test(tab_style)
chi$stdres
```

#### audio
```{r}
tab_style  <- with(data, table(cluster_a, party))
chi <- chisq.test(tab_style)
chi$stdres
```

#### audiovisual
```{r}
tab_style  <- with(data, table(cluster_va, party))
chi <- chisq.test(tab_style)
chi$stdres
```

#### topic
```{r}
tab_style  <- with(data, table(topic, party))
chi <- chisq.test(tab_style)
chi$stdres
```

### Style x Party in Engagement (Voting)
### likes

#### visual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_v+party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
library(fixest)
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(post_likes ~ cluster_v | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_v", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
v1 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
#ggsave("f_poll_model__visual_N398.png", dpi = 600, width = 8, height = 6)
```


#### audio
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  #filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_a*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(post_likes ~ cluster_a | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_a", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```


#### audiovisual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  #filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_va + party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(post_likes ~ cluster_va | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_va", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### topic
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ topic*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(post_likes ~ topic | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```

```{r}
pred <- ggpredict(model_l, terms = c("topic", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### Voting va
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_va + party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(post_likes ~ cluster_va | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```

#### v + a + t
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_v + cluster_a + topic + party + (1 | name), data = combined3, family = 
                     nbinom2)

# combined3$cluster_v <- relevel(combined3$cluster_v, ref = "happy")
# combined3$cluster_a <- relevel(combined3$cluster_a, ref = "happy")
#combined3$topic <- relevel(combined3$topic, ref = "Voting")


summary(model_l)
```

#### demean ver.
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(post_likes ~ cluster_v + cluster_a + topic | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)

check_overdispersion(m_nb_fe)
```

### comments

#### visual
```{r}
combined3 <- data %>%
  #filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_v*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
# combined3 <- data %>%
#   mutate(party = as.factor(party))
# 
# # Poisson FE with candidate fixed effects
# m_fe_pois <- fepois(comment_count ~ cluster_v | name, data = combined3)
# 
# # Clustered SEs (candidate-level)
# etable(m_fe_pois, se = "cluster", cluster = ~ name)
# 
# check_overdispersion(m_fe_pois)
```

#### demean ver.
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(comment_count ~ cluster_v | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```


```{r}
pred <- ggpredict(model_l, terms = c("cluster_v", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audio
```{r}
combined3 <- data %>%
  #filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_a*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(comment_count ~ cluster_a | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_a", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audiovisual
```{r}
combined3 <- data %>%
  #filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_va+party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(comment_count ~ cluster_va | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_va", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### topic
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ topic*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(comment_count ~ topic | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```

```{r}
pred <- ggpredict(model_l, terms = c("topic", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_va+party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(comment_count ~ cluster_va | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```

#### v + a + t
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_v + cluster_a + topic + party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

#### demean ver.
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

m_nb_fe <- fenegbin(comment_count ~ cluster_v + cluster_a + topic | name,
                    data = combined3)
etable(m_nb_fe, se = "cluster", cluster = ~ name)
```

### comment sentiments
#### positive
##### visual
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ cluster_v*party + (1|name), data = combined3)
summary(model)
coefs <- extract_lmer_coefs(model)
coefs
```

```{r}
pred <- ggpredict(model, terms = c("cluster_v", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
v3 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment positivity"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

##### audio
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ cluster_a*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

```{r}
pred <- ggpredict(model, terms = c("cluster_a", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment positivity"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ cluster_va*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

```{r}
pred <- ggpredict(model, terms = c("cluster_va", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment positivity"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### neutral
##### visual
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neu ~ cluster_v*party + (1|name), data = combined3)
summary(model)
coefs <- extract_lmer_coefs(model)
coefs
```

##### audio
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neu ~ cluster_a*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```


##### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neu ~ cluster_va*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```


#### negative
##### visual
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neg ~ cluster_v*party + (1|name), data = combined3)
summary(model)
coefs <- extract_lmer_coefs(model)
coefs
```

##### audio
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neg ~ cluster_a*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```


##### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neg ~ cluster_va*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

#### topic
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ topic*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
coefs
```


```{r}
pred <- ggpredict(model, terms = c("topic", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment positivity"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

### poll
#### visual
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(poll_norm ~ cluster_v*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
coefs
```

```{r}
pred <- ggpredict(model, terms = c("cluster_v", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
p1 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted poll support"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audio
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(poll_norm ~ cluster_a*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
coefs
```

```{r}
pred <- ggpredict(model, terms = c("cluster_a", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment positivity"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Voting") %>%
  mutate(party = as.factor(party))

model <- lmer(poll_norm ~ cluster_va*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
coefs
```

```{r}
pred <- ggpredict(model, terms = c("cluster_va", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment positivity"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```


#### topic
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

model <- lmer(poll_norm ~ topic*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
coefs
```


```{r}
pred <- ggpredict(model, terms = c("topic", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment positivity"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```


=================================================================================
### Style x Party (Immigration)
### likes
#### visual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_v*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_v", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
#ggsave("f_poll_model__visual_N398.png", dpi = 600, width = 8, height = 6)
```


#### audio
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_a*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_a", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```


#### audiovisual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_va*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("cluster_va", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```


### comments
#### visual
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_v*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_v", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
v2 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audio
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_a*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("cluster_a", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
a2 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_va*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("cluster_va", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
fva2 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### topic
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ topic*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("topic", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

### comment sentiments
#### positive
##### visual
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ cluster_v*party + (1|name), data = combined3)
summary(model)
coefs <- extract_lmer_coefs(model)
coefs
```

##### audio
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ cluster_a*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ cluster_va*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```


#### neutral
##### visual
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neu ~ cluster_v*party + (1|name), data = combined3)
summary(model)
coefs <- extract_lmer_coefs(model)
coefs
```

##### audio
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neu ~ cluster_a*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neu ~ cluster_va*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

### negative
##### visual
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neg ~ cluster_v*party + (1|name), data = combined3)
summary(model)
coefs <- extract_lmer_coefs(model)
coefs
```

##### audio
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neg ~ cluster_a*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Immigration") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neg ~ cluster_va*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```


### Style x Party (Abortion)
### likes
#### visual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_v*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_v", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
v1 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
#ggsave("f_poll_model__visual_N398.png", dpi = 600, width = 8, height = 6)
```


#### audio
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_a*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_a", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
a1 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```


#### audiovisual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_va*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("cluster_va", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
fva1 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```


### comments
#### visual
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_v*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_v", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
v2 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audio
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_a*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("cluster_a", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
a2 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_va*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("cluster_va", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
fva2 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### topic
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ topic*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("topic", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

### comment sentiments
#### positive
##### visual
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ cluster_v*party + (1|name), data = combined3)
summary(model)
coefs <- extract_lmer_coefs(model)
coefs
```

##### audio
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ cluster_a*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ cluster_va*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```


#### neutral
##### visual
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neu ~ cluster_v*party + (1|name), data = combined3)
summary(model)
coefs <- extract_lmer_coefs(model)
coefs
```

##### audio
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neu ~ cluster_a*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neu ~ cluster_va*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

### negative
##### visual
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neg ~ cluster_v*party + (1|name), data = combined3)
summary(model)
coefs <- extract_lmer_coefs(model)
coefs
```

##### audio
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neg ~ cluster_a*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```

##### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Abortion") %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_neg ~ cluster_va*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
summary(model)
coefs
```


#### topic
```{r}
combined3 <- data %>%
  mutate(party = as.factor(party))

model <- lmer(comment_score_pos ~ topic*party + (1|name), data = combined3)
coefs <- extract_lmer_coefs(model)
coefs
```


```{r}
pred <- ggpredict(model, terms = c("topic", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment positivity"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

### Style x Party (Economics)
### likes
#### visual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Economic") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_v*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_v", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
v1 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
#ggsave("f_poll_model__visual_N398.png", dpi = 600, width = 8, height = 6)
```


#### audio
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Economic") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_a*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_a", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
a1 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```


#### audiovisual
```{r}
combined3 <- data %>%
  filter(post_likes != -1) %>%
  filter(topic == "Economic") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(post_likes ~ cluster_va*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("cluster_va", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
fva1 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted like counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```


### comments
#### visual
```{r}
combined3 <- data %>%
  filter(topic == "Economic") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_v*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```

```{r}
pred <- ggpredict(model_l, terms = c("cluster_v", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
v2 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audio
```{r}
combined3 <- data %>%
  filter(topic == "Economic") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_a*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("cluster_a", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
a2 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```

#### audiovisual
```{r}
combined3 <- data %>%
  filter(topic == "Economic") %>%
  mutate(party = as.factor(party))

model_l <- glmmTMB(comment_count ~ cluster_va*party + (1 | name), data = combined3, family = nbinom2)
summary(model_l)
```


```{r}
pred <- ggpredict(model_l, terms = c("cluster_va", "party")) %>%
  as.data.frame() %>%
  mutate(party = group)

x_levels <- pred %>%
  filter(party == "Republican") %>%
  arrange(desc(predicted)) %>%
  pull(x)

pred <- pred %>%
  mutate(x = factor(x, levels = x_levels))

# Plot
fva2 <- ggplot(pred, aes(x = x, y = predicted, fill = party)) +
  geom_col(position = position_dodge(width = 0.7), width = 0.6, color = "black") +
  geom_errorbar(aes(ymin = predicted, ymax = conf.high),
                position = position_dodge(width = 0.7), width = 0.3) +
  scale_fill_manual(values = c("Republican" = "#f8766d", "Democratic" = "#729fed")) +
  labs(
    x = "",
    y = "Predicted comment counts"
  ) +
  coord_flip()+
  scale_y_continuous(expand = c(0,0)) +
  theme_bw() +
  theme(
    plot.title = element_text(face = "bold", size = 16),
    plot.subtitle = element_text(margin = margin(b = 10), size = 12),
    panel.grid.major.y = element_line(color = "#ecf0f1"),
    plot.margin = margin(1, 1, 1, 1, "cm"),
    axis.text.x = element_text(size = 12),
    strip.text.x = element_text(size = 12),
    axis.text.y = element_text(size = 12),
    axis.title = element_text(size = 14),
    panel.grid.minor = element_blank()
  )
```
### visualization
```{r}
fv <- ggarrange(v1, v2, nrow = 2, common.legend = TRUE, legend="bottom")
annotate_figure(fv, , top = text_grob("Visual", face = "bold", size = 14))
#ggsave("figure_v.png", dpi = 600, width = 6, height = 8)
```

```{r}
f1 <- ggarrange(a1, a2, nrow = 2, common.legend = TRUE, legend="bottom") 
annotate_figure(f1, , top = text_grob("Audio", face = "bold", size = 14))
#ggsave("figure_a.png", dpi = 600, width = 6, height = 8)
```

```{r}
fva <- ggarrange(fva1, fva2, nrow = 2, common.legend = TRUE, legend="bottom")
annotate_figure(fva , top = text_grob("Audiovisual", face = "bold", size = 14))
ggsave("figure_va.png", dpi = 600, width = 6, height = 8)
```
